MaxEnt: What is it good for?

### 2015-06-28 ms.tex
Some edits

\subsection{The ``constraint rule'' controversy}
Is it valid to use an experimental average (literally the arithmetic mean of
some data) to set the expected value of a probability distribution? The
assumption that this is okay has been termed {\it the constraint rule}
\citep{uffink}.

In many presentations of MaxEnt, it is assumed that this is not a problem
({\bf cite people}). Other authors have noticed that it's possible to
condition on the observed arithmetic mean, as one would do in a standard
Bayesian analysis of that information, and that this can lead to a different
answer from the constraint rule.

>>>>

\subsection{The ``constraint rule'' controversy}
Is it valid to use an experimental average (literally the arithmetic mean of
some data) to set the expected value of a probability distribution? The
assumption that this is okay has been termed {\it the constraint rule}, which
has been discussed in depth by \citet{uffink}.

In many presentations of MaxEnt, it is assumed that this is not a problem.
For example, \citet{jaynes} often motivated MaxEnt using an example of a
non-standard six-sided die, and we are asked to assign a probability
distribution for the result of the next toss, using the information that the
historical average of the tosses is 4.5 instead of the 3.5 one would
usually expect.

Other authors have noticed that it's possible to
condition on the observed arithmetic mean, as one would do in a standard
Bayesian analysis of that information, and that this can lead to a different
answer from the constraint rule.
